---
title: "ACS age"
author: "jotunnch"
date: "February 1, 2020"
output: html_document
---

```{r}
library(tidycensus)
library(tidyverse)
library(janitor)
library(readxl)
library(ggrepel)
library(mapview)
library(tigris)
library(sf)
options(tigris_use_cache = TRUE)
library(gganimate)
```

Did stuff with the 2010 census data and got the data figured out.
Now going to do the ACS data so I can have more up to date data.

```{r}

v18 <- load_variables(2018, "acs5", cache = TRUE)

total_med_age <- "B01002_001"

king19 <- get_acs(geography = "tract", variables = c(median_age = total_med_age), state = "WA", county = "King", geometry = TRUE, keep_geo_vars = TRUE)


```

Make some quick functions
```{r}
clean_census <- function(x, remove_king_water = TRUE) {
  
  if (remove_king_water) {
    x <- remove_water(x)
  }
  
  x %>%
  clean_names() %>%
  separate(name_y, into = c("tract", "county", "state"), sep = ",") %>%
  mutate(tract = str_extract(tract, "\\d+\\.?\\d?\\d?$"),
         county = str_remove(county, " County"))
}

make_seattle_only <- function(x) {
  seattle_data <- read_excel("SeattleCensusBlocksandNeighborhoodCorrelationFile.xlsx")

  seattle_tracts <- seattle_data %>%
    clean_names() %>%
    select(tract_10, urban_village_name, cra_name, neighborhoods_included, neighborhood_district_name) %>%
    mutate(tract = str_replace(as.character(tract_10), "(\\d+)(\\d\\d)$", "\\1\\.\\2") %>%
             str_replace("(\\d+)\\.00", "\\1")) %>%
    select(tract, everything(), -tract_10) %>%
    filter(tract != "9901") # this is water around vashon island

  x %>%
  semi_join(seattle_tracts, by = "tract")
}

remove_water <- function(x) {
  # get the water
  king_water <- area_water("WA", "King", class = "sf")
  
  st_difference(x, st_union(st_combine(king_water), by_feature = TRUE))
}
```

Check function
```{r}
cking19 <- king19 %>%
  clean_census()
```

```{r}
cking19

sea_mage19 <- make_seattle_only(cking19)

sea_mage19
```

```{r}
sea_mage19 %>%
  ggplot(aes(fill = estimate)) +
  geom_sf() +
  scale_fill_viridis_c() +
  theme_bw() +
  labs(fill = "age")

cking19 %>%
  ggplot(aes(fill = estimate)) +
  geom_sf() +
  scale_fill_viridis_c() +
  theme_bw() +
  labs(fill = "age")
```

## Going to try and grab multiple years
```{r}
total_med_age <- "B01002_001"
total_males <- "B01001_002"
total_females <- "B01001_026"
total_count <- "B01001_001"

all_years <- c(2011:2018)

king_years <- map(all_years, function(x) {
  get_acs(geography = "tract", variables = c(median_age = total_med_age,
                                             total_count = total_count,
                                             total_males = total_males,
                                             total_females = total_females),
          state = "WA", county = "King", 
          geometry = TRUE, keep_geo_vars = TRUE, year = x)
}
)
```

```{r}
cl_king_years <- king_years %>%
  map(clean_census)

sea_years <- cl_king_years %>%
  map(make_seattle_only) %>%
  map2(all_years, function(x, y) {
    x %>%
      mutate(year = y) %>%
      select(year, tract, county, state, variable, estimate, moe, geometry)
  })

sea_years <- do.call(rbind, sea_years)
  
```

```{r}
sea_years %>%
  filter(variable == "median_age") %>%
  ggplot(aes(fill = estimate)) +
  geom_sf() +
  scale_fill_viridis_c() +
  theme_bw() +
  labs(fill = "age") +
  facet_wrap(~year)

ggsave("age_over_time.pdf", height = 9, width = 9)
```

I'm going to add in some more variables: counts for males and females.
```{r}
sea_years %>%
  filter(variable == "total_count") %>%
  ggplot(aes(fill = estimate)) +
  geom_sf() +
  scale_fill_viridis_c(option = "magma") +
  theme_bw() +
  labs(fill = "population") +
  facet_wrap(~year)

ggsave("total_count_over_time.pdf", height = 9, width = 9)
  
```

Going to try this with gganimate
Geometries are changing over time, need to standardize these.
```{r}
sea_years_geo <- sea_years %>%
  filter(year == "2018") %>%
  select(tract, geometry) %>%
  distinct(tract, keep.all = TRUE) %>%
  right_join(st_drop_geometry(sea_years), by = "tract")

saveRDS(sea_years_geo, "seattle_acs_sf_obj.rds")  

sea_years_geo_anim <- sea_years_geo %>%
  filter(variable == "total_count") %>%
  ggplot(aes(fill = estimate)) +
  geom_sf() +
  scale_fill_viridis_c(option = "magma") +
  theme_bw() +
  labs(fill = "population", title = "Changing Times: Seattle Population", subtitle = "Year: {closest_state}", caption = "By Jotunn Ciderhouse\nData: American Community Survey") +
  annotate(geom = "curve", x = -122.42, y = 47.54,
           xend = -122.39, yend = 47.57,
           curvature = -0.3, arrow = arrow(length = unit(4, "mm"))) +
  annotate(geom = "text", x = -122.42, y = 47.54, label = "west\nseattle", vjust = 1, size = 8) +
  annotate(geom = "curve", x = -122.245, y = 47.715,
           xend = -122.335, yend = 47.68,
           curvature = -0.3, arrow = arrow(length = unit(4, "mm"))) +
  annotate(geom = "text", x = -122.245, y = 47.715, label = "green\nlake", vjust = -0.1, size = 8) +
  annotate(geom = "curve", x = -122.245, y = 47.62,
           xend = -122.315, yend = 47.62,
           curvature = -0.1, arrow = arrow(length = unit(4, "mm"))) +
  annotate(geom = "text", x = -122.245, y = 47.62, label = "capitol hill", vjust = -0.3, size = 8) +
  annotate(geom = "curve", x = -122.25, y = 47.585,
           xend = -122.27, yend = 47.57,
           curvature = -0.1, arrow = arrow(length = unit(4, "mm"))) +
  annotate(geom = "text", x = -122.25, y = 47.585, label = "columbia\ncity", vjust = -0.1, size = 8) +
  annotate(geom = "curve", x = -122.24, y = 47.655,
           xend = -122.295, yend = 47.65,
           curvature = -0.3, arrow = arrow(length = unit(4, "mm"))) +
  annotate(geom = "text", x = -122.24, y = 47.655, label = "uw", vjust = -0.3, size = 8) +
  annotate(geom = "curve", x = -122.42, y = 47.72,
           xend = -122.3875, yend = 47.67,
           curvature = 0.4, arrow = arrow(length = unit(4, "mm"))) +
  annotate(geom = "text", x = -122.42, y = 47.72, label = "ballard", vjust = -0.3, size = 8) +
  annotate(geom = "curve", x = -122.425, y = 47.62,
           xend = -122.3475, yend = 47.62,
           curvature = 0.2, arrow = arrow(length = unit(4, "mm"))) +
  annotate(geom = "text", x = -122.425, y = 47.62, label = "south lake\nunion", vjust = -0.1, size = 8) +
  annotate(geom = "curve", x = -122.375, y = 47.605,
           xend = -122.3475, yend = 47.61,
           curvature = 0.1, arrow = arrow(length = unit(4, "mm"))) +
  annotate(geom = "text", x = -122.375, y = 47.605, label = "downtown", hjust = 1.05, size = 8) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(size = 32),
        plot.subtitle = element_text(size = 24),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 18)) +
  transition_states(year,
                   transition_length = 4,
                   state_length = 1) +
  enter_fade()

animate(sea_years_geo_anim, height = 1200, width = 850)  

anim_save("sea_pop_heatmap3.gif")
```


```{r}
sea_years_geo %>%
  filter(variable == "total_count", year == "2018") %>%
  ggplot() +
  geom_sf(aes(fill = estimate)) +
  scale_fill_viridis_c(option = "magma") +
  theme_bw() +
  labs(fill = "population", title = "Seattle Population", subtitle = "Year: 2018", caption = "By Jotunn Ciderhouse\nData: American Community Survey") +
  annotate(geom = "curve", x = -122.42, y = 47.54,
           xend = -122.39, yend = 47.57,
           curvature = -0.3, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.42, y = 47.54, label = "west\nseattle", vjust = 1) +
  annotate(geom = "curve", x = -122.245, y = 47.715,
           xend = -122.335, yend = 47.68,
           curvature = -0.3, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.245, y = 47.715, label = "green\nlake", vjust = -0.1) +
  annotate(geom = "curve", x = -122.245, y = 47.62,
           xend = -122.315, yend = 47.62,
           curvature = -0.1, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.245, y = 47.62, label = "capitol hill", vjust = -0.3) +
  annotate(geom = "curve", x = -122.25, y = 47.585,
           xend = -122.27, yend = 47.57,
           curvature = -0.1, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.25, y = 47.585, label = "columbia\ncity", vjust = -0.1) +
  annotate(geom = "curve", x = -122.24, y = 47.655,
           xend = -122.295, yend = 47.65,
           curvature = -0.3, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.24, y = 47.655, label = "uw", vjust = -0.3) +
  annotate(geom = "curve", x = -122.42, y = 47.72,
           xend = -122.3875, yend = 47.67,
           curvature = 0.4, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.42, y = 47.72, label = "ballard", vjust = -0.3) +
  annotate(geom = "curve", x = -122.425, y = 47.62,
           xend = -122.3475, yend = 47.62,
           curvature = 0.2, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.425, y = 47.62, label = "south lake\nunion", vjust = -0.1) +
  annotate(geom = "curve", x = -122.375, y = 47.605,
           xend = -122.3475, yend = 47.61,
           curvature = 0.1, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.375, y = 47.605, label = "downtown", hjust = 1.05)
```



```{r}
sea_years %>%
  filter(variable == "total_count", year == "2018") %>%
  mapview(zcol = "estimate", legend = TRUE)
```

## Look at neighborhoods that are changing
```{r}
 
seattle_data <- read_excel("SeattleCensusBlocksandNeighborhoodCorrelationFile.xlsx")

seattle_tracts <- seattle_data %>%
  clean_names() %>%
  select(tract_10, urban_village_name, cra_name, neighborhoods_included, neighborhood_district_name) %>%
  mutate(tract = str_replace(as.character(tract_10), "(\\d+)(\\d\\d)$", "\\1\\.\\2") %>%
           str_replace("(\\d+)\\.00", "\\1")) %>%
  select(tract, everything(), -tract_10) %>%
  filter(tract != "9901") %>% # this is water around vashon island
  group_by(tract, cra_name) %>%
  tally() %>%
  select(-n) %>%
  ungroup()
```

```{r}
sea_years_geo %>%
  filter(year == 2018, variable == "total_count") %>%
  left_join(seattle_tracts, by = "tract") %>%
  ggplot(aes(y = estimate, x = fct_reorder(tract, estimate))) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - moe, ymax = estimate + moe)) +
  coord_flip()
  
```

```{r}
sea_years_geo_neigh <- sea_years_geo %>%
  left_join(seattle_tracts, by = "tract")

sea_years_geo_neigh %>%
  filter(year == 2018, variable == "total_count") %>%
  ggplot(aes(y = estimate, x = fct_reorder(tract, estimate))) +
  geom_point(col = "green") +
  geom_errorbar(aes(ymin = estimate - moe, ymax = estimate + moe)) +
  geom_point(data = filter(sea_years_geo_neigh, year == 2011, variable == "total_count"), col = "blue") +
  geom_errorbar(data = filter(sea_years_geo, year == 2011, variable == "total_count"), aes(ymin = estimate - moe, ymax = estimate + moe)) +
  coord_flip()

sea_years_geo_neigh %>%
  filter(year == 2011 | year == 2018, variable == "total_count") %>%
  ggplot(aes(y = estimate, x = fct_reorder(tract, estimate, max), col = as.factor(year), label = cra_name)) +
  geom_point() +
  geom_text_repel(data = filter(sea_years_geo_neigh, year == 2011 | year == 2018, variable == "total_count") %>% arrange(tract, -estimate) %>% distinct(tract, .keep_all = TRUE), hjust = 1) +
  coord_flip()

ggsave("test.pdf", width = 12, height = 12)

sea_years_diff <- sea_years_geo_neigh %>%
  filter(year == 2011 | year == 2018, variable == "total_count") %>%
  select(-moe) %>%
  spread(key = year, value = estimate) %>%
  clean_names() %>%
  mutate(count_diff = x2018 - x2011,
         prc_count_incr = count_diff/x2011*100) %>%
  arrange(-count_diff) 

top10_count_diff <- sea_years_diff %>%
  pull(tract) %>%
  .[1:10]

sea_years_geo_neigh %>%
  filter(year == 2011 | year == 2018, variable == "total_count") %>%
  ggplot(aes(y = estimate, x = fct_reorder(tract, estimate*(year == 2011), max), label = cra_name)) +
  geom_col() +
  coord_flip() +
  transition_states(year,
                    transition_length = 2,
                    state_length = 1)
```

```{r}
top10_count_each_year <- sea_years_geo_neigh %>%
  filter(variable == "total_count") %>%
  group_by(year) %>%
  mutate(rank = rank(-estimate)) %>%
  filter(rank <= 10) %>%
  pull(tract) %>%
  unique()
  

bar_anim <- sea_years_geo_neigh %>%
  filter(variable == "total_count", tract %in% top10_count_each_year) %>%
  group_by(year) %>%
  mutate(rank = rank(-estimate),
         est_label = as.character(round(estimate))) %>%
  ungroup() %>%
  ggplot() +
  geom_tile(aes(x = rank,
                y = estimate/2, 
                height = estimate,
                fill = as.factor(tract)
                ),
            width = 0.9,
            alpha = 0.8) +
 # geom_text(aes(y = 0, label = paste(tract, " ")), vjust = 0.2, hjust = 1) +
  geom_text(aes(x = rank, y = estimate, label = est_label), size = 6, hjust = -0.15) +
  geom_text(aes(x = rank, y = estimate, label = paste0("Tract ", tract, " (", cra_name, ")")), size = 6, color = "white", hjust = 1.05) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_x_reverse() +
  theme_classic() +
  labs(title = "Seattle: {closest_state}", x = "", y = "ACS population count estimate",
       caption = "by Jotunn Ciderhouse") +
  theme(legend.position = "none",
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 32),
        plot.margin = margin(0.5, 2, 0.5, 0.5, "cm"),
        axis.text.x = element_text(size = 18),
        axis.title.x = element_text(size = 18)) +
  transition_states(year, transition_length = 2, state_length = 1) +
  ease_aes("cubic-in-out")

animate(bar_anim, height = 800, width = 500, nframes = 200)
  
anim_save("top10_count_sea_neighborhoods.gif")  
```

## Trying dot density plots
```{r}
sea_years_geo_neigh %>%
  filter(variable == "total_females" | variable == "total_males", year == 2018) %>%
  select(-moe) %>%
  spread(key = variable, value = estimate) %>%
  mutate(prop_females = total_females / (total_males + total_females),
         prop_males = 1 - prop_females,
         tract = fct_reorder(tract, prop_females, max)) %>%
  select(-total_females, -total_males) %>%
  gather(key = "variable", value = "estimate", prop_females, prop_males) %>%
  ggplot(aes(x = tract, y = estimate, fill = variable)) +
  geom_col() +
  geom_hline(yintercept = 0.5) +
  coord_flip()

sea_sex_dots <- map(c("total_females", "total_males"), function(group) {
  sea_years_geo_neigh %>%
    filter(variable == group, year == 2018) %>%
    st_sample(., size = round(.$estimate / 50)) %>%
    st_sf() %>%
    mutate(group = group)
  }) %>%
  reduce(rbind)

sea_sex_dots_shuffle <- sample_frac(sea_sex_dots, size = 1) %>%
  mutate(group = fct_recode(group, Females = "total_females", Males = "total_males"))

plot(sea_sex_dots_shuffle, key.pos = 1)

ggplot() +
  geom_sf(data = sea_years_geo_neigh) +
  geom_sf(data = sea_sex_dots_shuffle, aes(color = group, fill = group), size = 0.5, alpha = 0.5) +
  theme_bw() +
  labs(title = "Estimated distribution of males and females in Seattle",
       subtitle = "2018 ACS Data",
       caption = "by Jotunn Ciderhouse") +
  guides(fill = guide_legend("Each dot equals\n50 people")) +
  scale_color_discrete(guide = FALSE) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  annotate(geom = "curve", x = -122.42, y = 47.54,
           xend = -122.39, yend = 47.57,
           curvature = -0.3, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.42, y = 47.54, label = "west\nseattle", vjust = 1) +
  annotate(geom = "curve", x = -122.245, y = 47.715,
           xend = -122.335, yend = 47.68,
           curvature = -0.3, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.245, y = 47.715, label = "green\nlake", vjust = -0.1) +
  annotate(geom = "curve", x = -122.245, y = 47.62,
           xend = -122.315, yend = 47.62,
           curvature = -0.1, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.245, y = 47.62, label = "capitol hill", vjust = -0.3) +
  annotate(geom = "curve", x = -122.25, y = 47.585,
           xend = -122.27, yend = 47.57,
           curvature = -0.1, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.25, y = 47.585, label = "columbia\ncity", vjust = -0.1) +
  annotate(geom = "curve", x = -122.24, y = 47.655,
           xend = -122.295, yend = 47.65,
           curvature = -0.3, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.24, y = 47.655, label = "uw", vjust = -0.3) +
  annotate(geom = "curve", x = -122.42, y = 47.72,
           xend = -122.3875, yend = 47.67,
           curvature = 0.4, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.42, y = 47.72, label = "ballard", vjust = -0.3) +
  annotate(geom = "curve", x = -122.425, y = 47.62,
           xend = -122.3475, yend = 47.62,
           curvature = 0.2, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.425, y = 47.62, label = "south lake\nunion", vjust = -0.1) +
  annotate(geom = "curve", x = -122.375, y = 47.605,
           xend = -122.3475, yend = 47.61,
           curvature = 0.1, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.375, y = 47.605, label = "downtown", hjust = 1.05)
  
ggsave("dot_density_sex_seattle.png", height = 9, width = 7)  
```

Doing above for 2011
```{r}
sea_sex_dots2 <- map(c("total_females", "total_males"), function(group) {
  sea_years_geo_neigh %>%
    filter(variable == group, year == 2011) %>%
    st_sample(., size = round(.$estimate / 50)) %>%
    st_sf() %>%
    mutate(group = group)
  }) %>%
  reduce(rbind)

sea_sex_dots_shuffle2 <- sample_frac(sea_sex_dots2, size = 1) %>%
  mutate(group = fct_recode(group, Females = "total_females", Males = "total_males"))

plot(sea_sex_dots_shuffle2, key.pos = 1)

ggplot() +
  geom_sf(data = sea_years_geo_neigh) +
  geom_sf(data = sea_sex_dots_shuffle2, aes(color = group, fill = group), size = 0.5, alpha = 0.5) +
  theme_bw() +
  labs(title = "Estimated distribution of males and females in Seattle",
       subtitle = "2011 ACS Data",
       caption = "by Jotunn Ciderhouse") +
  guides(fill = guide_legend("Each dot equals\n50 people")) +
  scale_color_discrete(guide = FALSE) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  annotate(geom = "curve", x = -122.42, y = 47.54,
           xend = -122.39, yend = 47.57,
           curvature = -0.3, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.42, y = 47.54, label = "west\nseattle", vjust = 1) +
  annotate(geom = "curve", x = -122.245, y = 47.715,
           xend = -122.335, yend = 47.68,
           curvature = -0.3, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.245, y = 47.715, label = "green\nlake", vjust = -0.1) +
  annotate(geom = "curve", x = -122.245, y = 47.62,
           xend = -122.315, yend = 47.62,
           curvature = -0.1, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.245, y = 47.62, label = "capitol hill", vjust = -0.3) +
  annotate(geom = "curve", x = -122.25, y = 47.585,
           xend = -122.27, yend = 47.57,
           curvature = -0.1, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.25, y = 47.585, label = "columbia\ncity", vjust = -0.1) +
  annotate(geom = "curve", x = -122.24, y = 47.655,
           xend = -122.295, yend = 47.65,
           curvature = -0.3, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.24, y = 47.655, label = "uw", vjust = -0.3) +
  annotate(geom = "curve", x = -122.42, y = 47.72,
           xend = -122.3875, yend = 47.67,
           curvature = 0.4, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.42, y = 47.72, label = "ballard", vjust = -0.3) +
  annotate(geom = "curve", x = -122.425, y = 47.62,
           xend = -122.3475, yend = 47.62,
           curvature = 0.2, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.425, y = 47.62, label = "south lake\nunion", vjust = -0.1) +
  annotate(geom = "curve", x = -122.375, y = 47.605,
           xend = -122.3475, yend = 47.61,
           curvature = 0.1, arrow = arrow(length = unit(2, "mm"))) +
  annotate(geom = "text", x = -122.375, y = 47.605, label = "downtown", hjust = 1.05)
```


Redid moving bar chart from above, but have it changing for sex as well now
```{r}
bar_anim <- sea_years_geo_neigh %>%
  filter(variable == "total_males" | variable == "total_females", tract %in% top10_count_each_year) %>%
#  group_by(year) %>%
 # mutate(rank = rank(-estimate),
 #        est_label = as.character(round(estimate))) %>%
#  ungroup() %>%
  mutate(tract = paste0("Tract ", tract, "\n(", cra_name, ")")) %>%
  ggplot() +
  geom_col(aes(x = tract, y = estimate, fill = variable), position = "stack") +
#  geom_text(aes(x = rank, y = estimate, label = paste0("Tract ", tract, " (", cra_name, ")")), size = 6, color = "white", hjust = 1.05) +
  coord_flip() +
#  scale_x_reverse() +
  theme_classic() +
  labs(title = "Seattle: {closest_state}", x = "", y = "ACS population count estimate",
       caption = "by Jotunn Ciderhouse") +
  scale_fill_discrete(name = "",
                      breaks = c("total_females", "total_males"),
                      labels = c("Females", "Males")) +
  theme(legend.position = "bottom",
        axis.ticks.y = element_blank(),
      #  axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 32),
        plot.margin = margin(0.5, 2, 0.5, 0.5, "cm"),
        axis.text.x = element_text(size = 18),
        axis.title.x = element_text(size = 18),
      axis.text.y = element_text(size = 14),
      legend.text = element_text(size = 14)) +
  transition_states(year, transition_length = 2, state_length = 1) +
  ease_aes("cubic-in-out")

animate(bar_anim, height = 800, width = 500, nframes = 200)

anim_save("top10_count_sea_neighborhoods_by_sex.gif")
```



## density
thinking of doing a dot plot that moves or grows? could do a line plot
```{r}
# calculating density
sea_years_geo_neigh$area <- st_area(sea_years_geo_neigh)

# gives it in square meters, want normal talk
sea_density <- sea_years_geo_neigh %>%
  filter(variable == "total_count") %>%
  mutate(sq_mi = as.numeric(area / 2.59e6),
         density = estimate / sq_mi)

sea_density %>%
  group_by(year) %>%
  arrange(-density)

sea_density %>%
  filter(year == 2011 | year == 2018) %>%
  ggplot(aes(x = density, y = fct_reorder(tract, density, max), color = as.factor(year))) +
  geom_point()

#nimbys vs yimbys
sea_density %>%
  st_drop_geometry() %>%
  filter(year == 2011 | year == 2018) %>%
  select(-moe, -estimate) %>%
  spread(key = "year", value = "density") %>%
  mutate(density_diff = `2018` - `2011`)
  ggplot(aes(x = density, y = fct_reorder(tract, density, max), color = as.factor(year))) +
  geom_point()

sea_density %>%
  ggplot() +
    geom_line(aes(x = year, y = density, group = tract))


```

